CODECHECK: An Open Science initiative for the independent execution of computations underlying research articles during peer review improves reproducibility

### 2021-02-09 codecheck-paper.tex
try to clarify

\textbf{How are failures during checks handled?}
We have not yet established a process for if a reproduction fails.  This
may simply reflect our biases in pre-selection of case studies.  In
the case that a journal adopts CODECHECK for all submissions, the open
question remains as what to do if a check fails, after exhausting
efforts between author and codechecker to reproduce the workflow.  A
negative comment in a CODECHECK certificate or a failed check does not
necessarily mean the paper or the science is bad (cf. discussion on
negative comments in \cite{everythinghertz123}).  We doubt that
publicly reporting failures (i.e.,~the code would not run) will
increase overall reproducibility, and we recommend sharing the latest
draft of the certificate only with the authors.  One must be careful
how policies on disclosing failures may \textbf{negatively impact the
  acceptance by authors}
%% SJE: what does this mean?
, and also how volunteer efforts may go unnoticed if no report is
published.  The most appropriate way forwards seems to be to give
private feedback for failures and public acknowledgment and
encouragement for successes.
% eLife's new model (see https://osf.io/9cftx/) will publish reports eventually, e.g.,~after preprint has been accepted elsewhere
Rosenthal et~al. \cite{Rosenthal2016b} discuss such incentives for different actors around the
implementation of reproducibility. We see CODECHECK as one way for
organisations to invest in reproducibility by creating incentives
until reproducible computations become the norm.

>>>>

\textbf{How are failures during checks handled?}
We have not yet established a process for if a reproduction fails.  This
may simply reflect our biases in pre-selection of case studies.  In
the case that a journal adopts CODECHECK for all submissions, the open
question remains as what to do if a check fails, after exhausting
efforts between author and codechecker to reproduce the workflow.  A
negative comment in a CODECHECK certificate or a failed check does not
necessarily mean the paper or the science is bad (cf. discussion on
negative comments in \cite{everythinghertz123}).  We doubt that
publicly reporting failures (i.e.,~the code would not run) will
increase overall reproducibility, and it may prohibit authors from
sharing their best efforts, which is always more desirable than
nothing shared. Therefore, we recommend sharing the latest
draft of the certificate only with the authors, even if that
means that volunteer efforts may go unnoticed if no report is
published.  The most appropriate way forwards seems to be to give
private feedback for failures, public acknowledgment and
encouragement for successes, and recognise codecheckers as reviewers.
% eLife's new model (see https://osf.io/9cftx/) will publish reports eventually, e.g.,~after preprint has been accepted elsewhere
Rosenthal et~al. \cite{Rosenthal2016b} discuss such incentives for different actors around the
implementation of reproducibility. We see CODECHECK as one way for
organisations to invest in reproducibility by creating incentives
until reproducible computations become the norm.
